% !TeX root = main.tex
\chapter*{Acknowledgements}

My foremost thanks go to my supervisor, Prof. Mark Plumbley, for his enthusiasm, encouragement, wisdom and guidance over
the years. Huge thanks also to my co-supervisors: Dr. Nick Bryan-Kinns, Dr. Janko \'{C}ali\'{c} and Prof.  David
Frohlich, for their invaluable suggestions, feedback and advice, and for helping me navigate an unfamiliar field of
research.

I have been extremely privileged to have been able to undertake this research as part of my employment at the BBC.  My
heartfelt thanks go out to Prof. Graham Thomas, Dr. Frank Melchior, Chris Pike and Samantha Chadwick for giving me this
rare opportunity, and for their steadfast support throughout the process.  Many thanks to my colleagues in the BBC R\&D
Audio Team for their patience, support and help with proofreading, but also for being brilliant people to work with.

This work was only made possible through the involvement of colleagues from BBC Radio, who volunteered their time
despite their demanding workload. My sincere thanks go to all of the radio producers who took the time to participate
in the user studies and contribute to the design of the interfaces. Thanks also to Deborah Cohen, Hugh Levinson and
John Goudie for allowing me access to their teams, and to Jonathan Glover his advocacy and encouragement.

Thanks to Liam Bowes, Carl Garner and Richard Sargeant from Anoto for their support in the development of the digital
pen interface, and to Matt Haynes and Matt Shotton from BBC R\&D, whose software formed part of the semantic speech
editor.

Finally, I'd personally like to thank my wife, Nancy, for her love, encouragement, patience and belief in me throughout
this process. I couldn't have done it without you.

\vfill
\noindent
The work in this thesis was fully funded by the British Broadcasting Corporation as part of the BBC Audio Research
Partnership.
