\chapter{Consent form}\label{app:consent}
You are invited to participate in this research study examining the performance
of audio waveforms. The purpose of this page is to provide you with information
required for you to make an informed decision regarding participation in this
research.

\paragraph{What you will be asked to do}
If you agree to participate in this experiment, you will be presented with a
sequence of nine audio recordings and asked to select the music within each
recording. The audio waveform will change throughout the experiment and you
will be asked to rate the performance of each. At the end, you will be asked to
compare them.

It is anticipated that the entire experiment will take between 10 and 15
minutes. You can complete the experiment at a time and location that is
convenient to you. You can also save your progress by creating a bookmark and
completing the experiment at a later date.

\paragraph{Voluntariness}
Participation in this study is voluntary. You may refuse to participate, refuse
to answer any questions or withdraw from the study at any time without any
consequences to you. If you wish to withdraw from the study after having
completed the task, you can do so by sending the ID code below, along with the
request to have your responses removed, to the researcher within 24 hours of
completion.

Your ID code is xxxxxx.

\paragraph{What information will be collected}
{\singlespacing
\begin{itemize}
\item Your browser and OS details
\item Your demographic information
\item Your actions during the tasks
\item Your ratings of the tasks and waveforms
\item The date/time you completed the tasks
\end{itemize}
}

\paragraph{Confidentiality}
No personally identifiable information will be collected during the experiment.
The data and results of this study may be published, but in no way that will
allow you to be identified.

\paragraph{Conditions}
To participate in this study your vision and hearing must be unimpaired and you
have to be at least 18 years old. There are no known or anticipated risks or
discomforts associated with participating in this study. You will not be
monetarily compensated for your participation in this research.

\paragraph{Further information}
If you require any further information regarding this research project or your
participation in the study you may contact Chris Baume
(\url{chris.baume@bbc.co.uk}).  The results of the experiment will be made
available on the following website:
\url{http://www.bbc.co.uk/rd/projects/audio-visualization}

\mbox{}\\
\noindent
\textbf{"I, the participant, have read the above information and wish to
  participate in this study"} [Agree/Disagree]
